REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-12-05 main.tex
Final revisions to appendix

\section{Methods}
\label{sec:methods}
In 
%mm brief, 
     summary, 
we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background. We 
%mm 
    assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
%mm
   as it forms
with the associated local gas abundances for each species. These methods are discussed in full detail below.

@@

%mm \subsubsection{Diffusive Heating}
         \subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of 
%mm diffusive 
   diffuse
heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and LW radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the LW radiation from the UV background, we account for localized LW flux from each of our stars to compute the total, local H$_2$ dissociation rates. Given the local LW flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of LW flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

@@

\section{Conclusion}
\textbf{You can ignore this for now, I'm saving it after the first iteration (AE)}
We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles. This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and LW radiation. This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UVB.

@@

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively. The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the \ion{H}{1} ionizing radiation photon energy (bottom left) and \ion{He}{1} ionizing photon energy (bottom right). We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and LW radiation bands.

The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid. A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency dependent absorption cross section. We tested this approach using the frequency dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision. Unlike the ionizing radiation, we assume constant FUV and LW band energies for each star, at 9.8 eV and 12.8 eV respectively.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{Q0}
\includegraphics[width=0.4\linewidth]{Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{L_FUV}
\includegraphics[width=0.4\linewidth]{L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{E0}
\includegraphics[width=0.4\linewidth]{E1}
\caption{Radiation properties for our model stars. Note, we only track radiation from stars above
8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure}

@@

Modeling supernova feedback with the injection of thermal energy alone can lead to rapid over cooling of the injected energy, and a significant underestimate of the effects of supernova feedback. Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time. However, physically consistent solutions have been employed \citep[e.g][]{Simpson2016} which inject a mixture of kinetic and thermal energy, whose ratio of kinetic to thermal energy injection depends on resolution and/or local gas density. This over cooling problem improves with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova. We take advantage of our high ($\sim$ pc) scale resolution and employ a simple thermal energy injection model for our supernova feedback. Here we demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.

The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the max (orange) and average (black) ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work. As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$. For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations. The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}, given as
\[
R_{\rm PDS} = 
\begin{cases*}
49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z $\le$ 0.01 \\
18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z $\ge$ 0.01 \\
\end{cases*}
\]
where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$. \citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region. In practice, the injection region is never uniform. We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each supernova. As shown, a majority of supernovae are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved. In general, these are supernova explosions from the most massive (i.e. most prompt) stars. We do not expect that resolving these supernovae will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here. In those, the supernovae are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{sn_density_hist}
\includegraphics[width=0.4\linewidth]{sn_radius_hist}
\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from the simulation. On the right, we give the distribution of the radius of the pressure driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region. The vertical lines give one and 4.5 cell widths. As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but a majority are resolved.}
\label{fig:supernova histogram}
\end{figure}

@@

\section{Cooling Rates}
\label{appendix:cooling}
Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling (dashed) and heating (dotted) rates at three characteristic densities for Z = 0.01 Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et. al. in prep). The solid lines give the absolute value of the net cooling rate, which more clearly indicates the regime at low temperatures where heating dominates. The curve as shown includes the z = 0 \citet{HM2012} metagalactic UVB.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_curve}
\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic background as modeled in \textsc{Cloudy}. The absolute value of the net cooling rate is shown with solid lines.}
\label{fig:cooling}
\end{figure}

We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons. First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used. The actual primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}. However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations. Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating. We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables. 
%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.

The cooling curves used in this work corrects a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations. Previous work in \citet{Hu2017} details this inconsistency. In short, adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates. We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives |cooling - heating| for our full model at $Z = 0.1~Z_{\odot}$ (black) as compared to a model using the optically thin metal line cooling rates (orange) at a range of densities. The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher. In low temperature regions, this can significantly shift the inferred equilibrium temperature.

The cooling curve shown in Figure~\ref{fig:cooling} avoids this discrepancy using re-computed metal line cooling tables. We have made these tables publicly available in the main distribution of \texttt{Grackle}. For densities where self-shielding is important, we computed \texttt{Cloudy} models of 1D clouds at each temperature and density pair with a physical size corresponding to the Jeans length. In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud. We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UVB. These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}. In computing these tables we had to include the CR ionization that dominates in optically thick clouds. Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions. We adopted a CR ionization rate of 10\% the MW value, though we note varying this from 1\% to 100\% the MW value did not have an effect on the extracted metal line cooling rates.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
\caption{The absolute value of the net cooling rate (|cooling - heating|) in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e. optically thin) metal line cooling rates. The regimes where heating dominates are plotted with dashed lines for clarity.}
\label{fig:cooling comparison}
\end{figure}

>>>>

\section{Methods}
\label{sec:methods}
In 
%mm brief, 
     summary, 
we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We 
%mm 
    assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
%mm
   as it forms
with the associated local gas abundances for each species. These methods are discussed in full detail below.

@@

%mm \subsubsection{Diffusive Heating}
         \subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of 
%mm diffusive 
   diffuse
heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates. Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

@@

\section{Conclusion}
\textbf{You can ignore this for now, I'm saving it after the first iteration (AE)}
We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles. This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation. This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UV background.

@@

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively. The stellar radiation properties are determined from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve 
%mm off of the OSTAR2002 grid) 
    for other stars,
given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Figure~\ref{fig:stellar radiation properties} we plot these properties. We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.

The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid. A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section. We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision. Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{Q0}
\includegraphics[width=0.4\linewidth]{Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{L_FUV}
\includegraphics[width=0.4\linewidth]{L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{E0}
\includegraphics[width=0.4\linewidth]{E1}
\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for \ion{H}{1} (bottom left) and \ion{He}{1} (bottom right). Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure}

@@

Modeling supernova feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of supernova feedback. Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time. However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density. 
%mm This overcooling problem improves 
   Overcooling becomes less important 
with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova. We take advantage of our high (parsec scale) resolution and employ a simple thermal energy injection model for our supernova feedback. We demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.

The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the peak and average ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work. As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$. For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations. The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
\[
R_{\rm PDS} = 
\begin{cases*}
49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z $\le$ 0.01 \\
18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z $\ge$ 0.01 \\
\end{cases*}
\]
where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$. \citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region. In practice, the injection region is never uniform. We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each supernova. As shown, a majority of supernovae are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved. In general, these are supernova explosions from the most massive (i.e. most prompt) stars. We do not expect that resolving these supernovae will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here. In those, the supernovae are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{sn_density_hist}
\includegraphics[width=0.4\linewidth]{sn_radius_hist}
\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the supernovae from the simulation. {\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region. The vertical lines show one and 4.5 cell widths. This shows that a fraction of these supernovae are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but the majority are well resolved.}
\label{fig:supernova histogram}
\end{figure}

@@

\section{Cooling and Heating Rates}
\label{appendix:cooling}

%mm moved this paragraph to the start of the section and rewrote accordingly.
To derive the diffuse cooling and heating rates used in the simulations, we make two approximations. First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal-line cooling and heating rates are used. The primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}. However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations. Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from Lyman-Werner dissociation, and ionization heating. We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables. 
%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.

Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et al.\ in prep). The 
%mm solid lines give the absolute value of the net cooling rate, which more clearly 
    Figure 
indicates the regime at low temperatures where heating dominates over cooling. The curve as shown includes 
%mm [it neglects local FUV]
   only
the $z = 0$ \citet{HM2012} metagalactic UV background.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_curve}
\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}. The absolute value of the net cooling
%mm
   or heating
rate is shown with solid lines.}
\label{fig:cooling}
\end{figure}

The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations. \citet{Hu2017} detail this inconsistency: adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates. We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate
%mm |cooling - heating| 
for our full model at $Z = 0.1$Z$_{\odot}$ as compared to a model using the optically thin metal line cooling rates at a range of densities. The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher. In low temperature regions, this can significantly shift the inferred equilibrium temperature.

The cooling curve shown in Figure~\ref{fig:cooling} avoids this discrepancy using re-computed metal line cooling tables. We have made these tables publicly available in the main distribution of \texttt{Grackle}. For densities where self-shielding is important, we computed \texttt{Cloudy} models of 1D clouds at each temperature and density pair with a physical size corresponding to the Jeans length. In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud. We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background. These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}. In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds. Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions. We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
\caption{The absolute value of the net cooling or heating rate 
%mm (|cooling - heating|)
 in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e. optically thin) metal line cooling rates. The regimes where heating dominates are plotted with dashed lines for clarity.}
\label{fig:cooling comparison}
\end{figure}
